namext
======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![R-check](https://github.com/ropenscilabs/namext/workflows/R-check/badge.svg)](https://github.com/ropenscilabs/namext/actions/)


`namext` - Extract scientific names from text using gnfinder

## Install gnfinder

gnfinder is required to use this package.

Installation instructions can be found at the [gnfinder repo](https://github.com/gnames/gnfinder). 

## Install namext

```{r eval=FALSE}
remotes::install_github("ropenscilabs/namext")
```

```{r}
library("namext")
```

## extract names

```{r}
x <- system.file("examples/BoegerEtal2015.pdf", package="namext")
name_extract(x)
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/namext/issues)
* License: MIT
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
